---
title: "Module_7"
author: "AGJ notes from RMIT"
date: "02/10/2017"
output: html_document
---

## Packages + Data

```{r}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
Body_temp <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1FV0Bw2BAM1EbedSW4SCU2G54ObxP0jA429GnDUlAO1g/edit?usp=sharing')
```

```{r}
Body_temp %>% summarise(Min = min(Body_temp,na.rm = TRUE),
                        Q1 = quantile(Body_temp,probs = .25,na.rm = TRUE),
                        Median = median(Body_temp, na.rm = TRUE),
                        Q3 = quantile(Body_temp,probs = .75,na.rm = TRUE),
                        Max = max(Body_temp,na.rm = TRUE),
                        Mean = mean(Body_temp, na.rm = TRUE),
                        SD = sd(Body_temp, na.rm = TRUE),
                        n = n(),
                        Missing = sum(is.na(Body_temp)))
```

```{r}
Body_temp$Body_temp %>% boxplot(ylab = "Temperature (Celsius)")
```
## Critical Value Approach + t sampling distribution
One tail test
```{r}
qt(p = 0.05, df = 130-1, lower.tail = TRUE)
```

```{r}
tcrittomean <- function(t ,mu, s, n) {
  se <- s/sqrt(n)
  x_bar <- mu + (t*se) #Determine critical mean
  return(x_bar)
}
```
This function can now be called:
```{r}
tcrittomean(t = qt(0.05, 130-1, lower.tail = TRUE),
     mu = 37, 
     s = sd(Body_temp$Body_temp),
     n = length(Body_temp$Body_temp))
```

## Title
Text
```{r}
qt(p = 0.05/2, df = 130-1, lower.tail = TRUE)
```
Text
```{r}
tcrittomean(t = qt(0.05/2,130-1,lower.tail = TRUE),
            mu = 37, 
            s = sd(Body_temp$Body_temp),
            n = length(Body_temp$Body_temp))
```
The upper critical mean
```{r}
tcrittomean(t = qt(1-(0.05/2),130-1,lower.tail = TRUE),
            mu = 37, 
            s = sd(Body_temp$Body_temp),
            n = length(Body_temp$Body_temp))
```


## p-value Approach
Text
```{r}
t_stat <- function(x_bar, mu, s, n){
  t <- (x_bar - mu)/(s/sqrt(n))
  return(t)
}
```

Text
```{r}
t <- t_stat(x_bar = mean(Body_temp$Body_temp),
       mu <- 37,
       s <- sd(Body_temp$Body_temp),
       n <- length(Body_temp$Body_temp))
t
```
We now calculate the exact pp-value using the pt() function:
```{r}
pt(q = t, df= 130 - 1)
```

```{r}
pt(q = t, df= 130 - 1)*2
```



## Confidence Interval Approach
Calculating CI in R
```{r}
t.test(Body_temp$Body_temp, conf.level = .95)$conf.int
```

## The one-sample tt-test in R
Text
```{r}
t.test(Body_temp$Body_temp, mu = 37, alternative="less")
```
Example of the two-tailed hypothesis test:
```{r}
t.test(Body_temp$Body_temp, mu = 37, alternative="two.sided")
```
You can also change the significance level. For example, α=0.01α=0.01 of a 99% CI:
```{r}
t.test(Body_temp$Body_temp, mu = 37, conf.level = .99, alternative="two.sided")
```

## Two-sample tt-tests - Body Temperatures Revisited
```{r}
Body_temp %>% group_by(Gender) %>% summarise(Min = min(Body_temp,na.rm = TRUE),
                                             Q1 = quantile(Body_temp,probs = .25,na.rm = TRUE),
                                             Median = median(Body_temp, na.rm = TRUE),
                                             Q3 = quantile(Body_temp,probs = .75,na.rm = TRUE),
                                             Max = max(Body_temp,na.rm = TRUE),
                                             Mean = mean(Body_temp, na.rm = TRUE),
                                             SD = sd(Body_temp, na.rm = TRUE),
                                             n = n(),
                                             Missing = sum(is.na(Body_temp)))
```

```{r}
Body_temp %>% boxplot(Body_temp ~ Gender, data = ., ylab = "Temperature (Celsius)")
```

Let’s look at the body temperature distributions for males and females using the  qqPlot() function.
```{r}
install.packages("car")
library(car)
Body_temp_male <- Body_temp %>% filter(Gender == 1)
Body_temp_male$Body_temp %>% qqPlot(dist="norm")
```

```{r}
Body_temp_female <- Body_temp %>% filter(Gender == 2)
Body_temp_female$Body_temp %>% qqPlot(dist="norm")
```


## Homogeneity of Variance
```{r}
leveneTest(Body_temp ~ Gender, data = Body_temp)
```


## Two-sample tt-test - Assuming Equal Variance
```{r}
t.test(
  Body_temp ~ Gender,
  data = Body_temp,
  var.equal = TRUE,
  alternative = "two.sided"
  )
```

Assuming α=0.05α=0.05 and a two-tailed test, we find t∗t∗ using the R function:
```{r}
qt(p = 0.025, df = 65 + 65 - 2)
```


## Two-sample tt-test - Assuming Unequal Variance
```{r}
t.test(
  Body_temp ~ Gender,
  data = Body_temp,
  var.equal = FALSE,
  alternative = "two.sided"
  )
```




# Prison Data

```{r}
PrisonStress %>% filter(Group == "Sport") %>%
  summarise(
  Min = min(PSSbefore, na.rm = TRUE),
  Q1 = quantile(PSSbefore, probs = .25, na.rm = TRUE),
  Median = median(PSSbefore, na.rm = TRUE),
  Q3 = quantile(PSSbefore, probs = .75, na.rm = TRUE),
  Max = max(PSSbefore, na.rm = TRUE),
  Mean = mean(PSSbefore, na.rm = TRUE),
  SD = sd(PSSbefore, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(PSSbefore))
  )
```

```{r}
PrisonStress %>% filter(Group == "Sport") %>%
  summarise(
  Min = min(PSSafter, na.rm = TRUE),
  Q1 = quantile(PSSafter, probs = .25, na.rm = TRUE),
  Median = median(PSSafter, na.rm = TRUE),
  Q3 = quantile(PSSafter, probs = .75, na.rm = TRUE),
  Max = max(PSSafter, na.rm = TRUE),
  Mean = mean(PSSafter, na.rm = TRUE),
  SD = sd(PSSafter, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(PSSafter))
  )
```

```{r}
PrisonStress <- PrisonStress %>% mutate(d = PSSafter - PSSbefore)
```

```{r}
PrisonStress %>% filter(Group == "Sport") %>%
  summarise(
  Min = min(d, na.rm = TRUE),
  Q1 = quantile(d, probs = .25, na.rm = TRUE),
  Median = median(d, na.rm = TRUE),
  Q3 = quantile(d, probs = .75, na.rm = TRUE),
  Max = max(d, na.rm = TRUE),
  Mean = mean(d, na.rm = TRUE),
  SD = sd(d, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(d))
  )
```

```{r}
PrisonStress_sport <- PrisonStress %>% filter(Group == "Sport")
qqPlot(PrisonStress_sport$d, dist="norm"
```


```{r}
t.test(PrisonStress_sport$PSSafter, PrisonStress_sport$PSSbefore,
       paired = TRUE,
       alternative = "two.sided")
```

```{r}
t.test(PrisonStress_sport$d, 
       mu = 0, 
       alternative = "two.sided")
```

```{r}
qt(p = 0.025, df = 14)
```

```{r}
2*pt(q = -2.68, df = 14)
```

## Paired Samples tt-test Visualisation

```{r}
boxplot(
  PrisonStress_sport$PSSbefore,
  PrisonStress_sport$PSSafter,
  ylab = "Stress Ratings",
  xlab = "Time"
  )
axis(1, at = 1:2, labels = c("Before", "After"))
```

```{r}
matplot(t(data.frame(PrisonStress_sport$PSSbefore, PrisonStress_sport$PSSafter)),
  type = "b",
  pch = 19,
  col = 1,
  lty = 1,
  xlab = "Time",
  ylab = "Stress Ratings",
  xaxt = "n"
  )
axis(1, at = 1:2, labels = c("Before", "After"))
```

```{r}
library(granova)
granova.ds(
  data.frame(PrisonStress_sport$PSSbefore, PrisonStress_sport$PSSafter),
  xlab = "Prison Stress - Before",
  ylab = "Prison Stress - After"
  )
```

```{r}

```























