---
title: "Module_8"
author: "AlistairGJ"
date: "15/10/2017"
output:
  html_notebook: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Heading

```{r opening the packages, eval=FALSE}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
random <- gsheet2tbl('https://docs.google.com/spreadsheets/d/13TLSLddeGF-k3ATVcG1vS38VtGKXg-dkwVEuEUKWY7g/edit?usp=sharing')
```

##### Question 1 (mod8q1) - Are the random numbers produced by RANDOM.ORG truly random? RANDOM.ORG generates true random number using atmospheric noise as opposed to the pseudo random number generator used by most computers. To test the “randomness” of RANDOM.ORG’s generator, 10,000 random integers between 0 and 9 were generated. The random numbers are contained in the Random.org.csv data file available from the data repository. Using this data, answer the following questions. Which of the following statistical tests is most appropriate in this situation?
* Use `table(dataset)` to check counts
* These counts will be considered as bands, can use Chi-square Goodness of Fit Test ("ordinal bands")
* *The Chi-square goodness of fit test is a hypothesis test in which we test if the count of our categorical observations “fit” the model of expected outcomes. In this example, the expected outcomes are based on the manufacturer’s claimed proportions.*
```{r mod8q1 explore, eval=TRUE}
table(random)
```
```{r mod8q1 ans}
mod8q1 <- "Chi-squared Goodness of Fit Test"
```

##### Question 2 (mod8q2) - Which one of the following hypotheses is the correct Alternate hypothesis for the statistical test chosen above?
* We woulduse the Chi-square statistic to test the following hypotheses at the standard 0.05 significance level
* H0 observed population distribution is consistent with the expected population distribution
* HA observed population distribution is NOT consistent with the expected population distribution
* We can use a χ2χ2 critical value or pp-value to decide whether to reject or fail to reject H0
```{r mod8q2 ans}
mod8q2 <- "HA: At least two random integers between 0 to 9 has a population proportion NOT equal to 0.1 b/c 'HA observed population distribution is NOT consistent with the expected population distribution' "
```

##### Question 3 (mod8q3) - Which one of the following hypotheses is the correct Null hypothesis for the statistical test chosen above?
```{r mod8q3 ans}
mod8q3 <- "H0: Each random integer between 0 to 9 has a population proportion = 0.1"
```

##### Question 4 (mod8q4) - Produce a frequency distribution of the random integers. Which integer was the most underrepresented?
```{r mod8q4a ans a}
mod8q4a <- table(random) %>% prop.table()
mod8q4a
```
Which integer is the most underrepresented?
```{r mod8q4a ans a_min}
min(mod8q4a)
```


```{r mod8q4b ans b}
mod8q4b <- c(0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1,0.1)
```
* Now run the Chi-square goodness of fit test using the previous table() and the chisq.test() function
```{r mod8q4c ans c}
mod8q4c <- chisq.test(table(random), p = mod8q4b)
mod8q4c
```
* Why?
```{r }
mod8q4c
```
```{r }
mod8q4c$expected
```
```{r }
mod8q4c$observed
```


```{r mod8q5 ans}
max(mod8q4a)
```

### Colour .csv

```{r opening the ds colour, eval=FALSE}
colour <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1xmZ40Dpn0bJ98cepa6ay-Ustl6cj7LlWibN5zEE3Syk/edit?usp=sharing')
```

```{r checking the table, eval=FALSE}
table(colour$Gender, colour$Eyes)
```

```{r, eval=FALSE}
table(colour$Gender, colour$Eyes) %>% prop.table(margin = 2)
```

```{r, eval=FALSE}
colour_chi <- chisq.test(table(colour$Gender, colour$Eyes))
colour_chi
```

```{r, eval=FALSE}
colour_chi$observed
```

```{r, eval=FALSE}
colour_chi$expected
```

```{r, eval=FALSE}
qchisq(p = .95,df = 3)
```











