---
title: "Module_7"
author: "AGJ notes from RMIT"
date: "02/10/2017"
output: html_document
---

## Packages + Data

```{r}
library(ggplot2)
library(dplyr)
library(gsheet)
library(vembedr)
library(gridExtra)
library("htmltools")
Body_temp <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1FV0Bw2BAM1EbedSW4SCU2G54ObxP0jA429GnDUlAO1g/edit?usp=sharing')
cars <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1oS7EsWOAYDoSwkSV4myvvPgkxamVavNsQeVLBb2BArw/edit?usp=sharing')
exer_depr <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1-dsxN6LeMrlpLLQ062iA6H3w9o4XrN1jMjSPkmjmFVA/edit?usp=sharing')
leg_press <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1jwh0T-RehDBw9QEh0ZU8gncfIWaQpPamkOZXRqkvCwo/edit?usp=sharing')
times <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1AX0iwJJa7HaolRblgjYrPdnd0GrJnWOrp6UYJZVMS6o/edit?usp=sharing')
```

```{r}
Body_temp %>% summarise(Min = min(Body_temp,na.rm = TRUE),
                        Q1 = quantile(Body_temp,probs = .25,na.rm = TRUE),
                        Median = median(Body_temp, na.rm = TRUE),
                        Q3 = quantile(Body_temp,probs = .75,na.rm = TRUE),
                        Max = max(Body_temp,na.rm = TRUE),
                        Mean = mean(Body_temp, na.rm = TRUE),
                        SD = sd(Body_temp, na.rm = TRUE),
                        n = n(),
                        Missing = sum(is.na(Body_temp)))
```

```{r}
Body_temp$Body_temp %>% boxplot(ylab = "Temperature (Celsius)")
```
## Critical Value Approach + t sampling distribution
One tail test
```{r}
qt(p = 0.05, df = 130-1, lower.tail = TRUE)
```

```{r}
tcrittomean <- function(t ,mu, s, n) {
  se <- s/sqrt(n)
  x_bar <- mu + (t*se) #Determine critical mean
  return(x_bar)
}
```
This function can now be called:
```{r}
tcrittomean(t = qt(0.05, 130-1, lower.tail = TRUE),
     mu = 37, 
     s = sd(Body_temp$Body_temp),
     n = length(Body_temp$Body_temp))
```

## Title
Text
```{r}
qt(p = 0.05/2, df = 130-1, lower.tail = TRUE)
```
Text
```{r}
tcrittomean(t = qt(0.05/2,130-1,lower.tail = TRUE),
            mu = 37, 
            s = sd(Body_temp$Body_temp),
            n = length(Body_temp$Body_temp))
```
The upper critical mean
```{r}
tcrittomean(t = qt(1-(0.05/2),130-1,lower.tail = TRUE),
            mu = 37, 
            s = sd(Body_temp$Body_temp),
            n = length(Body_temp$Body_temp))
```


## p-value Approach
Text
```{r}
t_stat <- function(x_bar, mu, s, n){
  t <- (x_bar - mu)/(s/sqrt(n))
  return(t)
}
```

Text
```{r}
t <- t_stat(x_bar = mean(Body_temp$Body_temp),
       mu <- 37,
       s <- sd(Body_temp$Body_temp),
       n <- length(Body_temp$Body_temp))
t
```
We now calculate the exact pp-value using the pt() function:
```{r}
pt(q = t, df= 130 - 1)
```

```{r}
pt(q = t, df= 130 - 1)*2
```



## Confidence Interval Approach
Calculating CI in R
```{r}
t.test(Body_temp$Body_temp, conf.level = .95)$conf.int
```

## The one-sample tt-test in R
Text
```{r}
t.test(Body_temp$Body_temp, mu = 37, alternative="less")
```
Example of the two-tailed hypothesis test:
```{r}
t.test(Body_temp$Body_temp, mu = 37, alternative="two.sided")
```
You can also change the significance level. For example, α=0.01α=0.01 of a 99% CI:
```{r}
t.test(Body_temp$Body_temp, mu = 37, conf.level = .99, alternative="two.sided")
```

## Two-sample tt-tests - Body Temperatures Revisited
```{r}
Body_temp %>% group_by(Gender) %>% summarise(Min = min(Body_temp,na.rm = TRUE),
                                             Q1 = quantile(Body_temp,probs = .25,na.rm = TRUE),
                                             Median = median(Body_temp, na.rm = TRUE),
                                             Q3 = quantile(Body_temp,probs = .75,na.rm = TRUE),
                                             Max = max(Body_temp,na.rm = TRUE),
                                             Mean = mean(Body_temp, na.rm = TRUE),
                                             SD = sd(Body_temp, na.rm = TRUE),
                                             n = n(),
                                             Missing = sum(is.na(Body_temp)))
```

```{r}
Body_temp %>% boxplot(Body_temp ~ Gender, data = ., ylab = "Temperature (Celsius)")
```

Let’s look at the body temperature distributions for males and females using the  qqPlot() function.
```{r}
install.packages("car")
library(car)
Body_temp_male <- Body_temp %>% filter(Gender == 1)
Body_temp_male$Body_temp %>% qqPlot(dist="norm")
```

```{r}
Body_temp_female <- Body_temp %>% filter(Gender == 2)
Body_temp_female$Body_temp %>% qqPlot(dist="norm")
```


## Homogeneity of Variance
```{r}
leveneTest(Body_temp ~ Gender, data = Body_temp)
```


## Two-sample tt-test - Assuming Equal Variance
```{r}
t.test(
  Body_temp ~ Gender,
  data = Body_temp,
  var.equal = TRUE,
  alternative = "two.sided"
  )
```

Assuming α=0.05α=0.05 and a two-tailed test, we find t∗t∗ using the R function:
```{r}
qt(p = 0.025, df = 65 + 65 - 2)
```


## Two-sample tt-test - Assuming Unequal Variance
```{r}
t.test(
  Body_temp ~ Gender,
  data = Body_temp,
  var.equal = FALSE,
  alternative = "two.sided"
  )
```




# Prison Data

```{r}
PrisonStress %>% filter(Group == "Sport") %>%
  summarise(
  Min = min(PSSbefore, na.rm = TRUE),
  Q1 = quantile(PSSbefore, probs = .25, na.rm = TRUE),
  Median = median(PSSbefore, na.rm = TRUE),
  Q3 = quantile(PSSbefore, probs = .75, na.rm = TRUE),
  Max = max(PSSbefore, na.rm = TRUE),
  Mean = mean(PSSbefore, na.rm = TRUE),
  SD = sd(PSSbefore, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(PSSbefore))
  )
```

```{r}
PrisonStress %>% filter(Group == "Sport") %>%
  summarise(
  Min = min(PSSafter, na.rm = TRUE),
  Q1 = quantile(PSSafter, probs = .25, na.rm = TRUE),
  Median = median(PSSafter, na.rm = TRUE),
  Q3 = quantile(PSSafter, probs = .75, na.rm = TRUE),
  Max = max(PSSafter, na.rm = TRUE),
  Mean = mean(PSSafter, na.rm = TRUE),
  SD = sd(PSSafter, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(PSSafter))
  )
```

```{r}
PrisonStress <- PrisonStress %>% mutate(d = PSSafter - PSSbefore)
```

```{r}
PrisonStress %>% filter(Group == "Sport") %>%
  summarise(
  Min = min(d, na.rm = TRUE),
  Q1 = quantile(d, probs = .25, na.rm = TRUE),
  Median = median(d, na.rm = TRUE),
  Q3 = quantile(d, probs = .75, na.rm = TRUE),
  Max = max(d, na.rm = TRUE),
  Mean = mean(d, na.rm = TRUE),
  SD = sd(d, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(d))
  )
```

```{r}
PrisonStress_sport <- PrisonStress %>% filter(Group == "Sport")
qqPlot(PrisonStress_sport$d, dist="norm")
```


```{r}
t.test(PrisonStress_sport$PSSafter, PrisonStress_sport$PSSbefore,
       paired = TRUE,
       alternative = "two.sided")
```

```{r}
t.test(PrisonStress_sport$d, 
       mu = 0, 
       alternative = "two.sided")
```

```{r}
qt(p = 0.025, df = 14)
```

```{r}
2*pt(q = -2.68, df = 14)
```

## Paired Samples tt-test Visualisation

```{r}
boxplot(
  PrisonStress_sport$PSSbefore,
  PrisonStress_sport$PSSafter,
  ylab = "Stress Ratings",
  xlab = "Time"
  )
axis(1, at = 1:2, labels = c("Before", "After"))
```

```{r}
matplot(t(data.frame(PrisonStress_sport$PSSbefore, PrisonStress_sport$PSSafter)),
  type = "b",
  pch = 19,
  col = 1,
  lty = 1,
  xlab = "Time",
  ylab = "Stress Ratings",
  xaxt = "n"
  )
axis(1, at = 1:2, labels = c("Before", "After"))
```

```{r}
library(granova)
granova.ds(
  data.frame(PrisonStress_sport$PSSbefore, PrisonStress_sport$PSSafter),
  xlab = "Prison Stress - Before",
  ylab = "Prison Stress - After"
  )
```


###Question 10  - Mean of Running Time (times) (NO check)
###Question 11  - DS of Running Time (times) (NO check)
```{r}
summary(times)
```

```{r}
times %>% summarise(Min = min(Time,na.rm = TRUE),
                        Q1 = quantile(Time,probs = .25,na.rm = TRUE),
                        Median = median(Time, na.rm = TRUE),
                        Q3 = quantile(Time,probs = .75,na.rm = TRUE),
                        Max = max(Time,na.rm = TRUE),
                        Mean = mean(Time, na.rm = TRUE),
                        SD = sd(Time, na.rm = TRUE),
                        n = n(),
                        Missing = sum(is.na(Time)))
```

https://statistics.berkeley.edu/computing/r-t-tests

### Question 14
```{r}
t.test(times$Time, mu = 14, alternative = "two.sided")
```


### Question 14
```{r}
t.test(times$Time, mu = 14, alternative="less")
```

### Question 14
```{r}
t.test(times$Time, mu = 14, conf.level = 0.95, alternative = NULL)
```
```{r}
t.test(times$Time, mu = 14, conf.level = 0.95, alternative="two.sided")
```
## Leg Press Data
```{r}
leg_press <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1jwh0T-RehDBw9QEh0ZU8gncfIWaQpPamkOZXRqkvCwo/edit?usp=sharing')
```

## Question 23 - State the Null Hypothesis

It is has been said that the average physically active adult can leg press 2 times their body weight. A researcher gathers a random sample of the population and tests their 1 repetition max kg (1RM) on a leg press machine. The researcher then divides the 1RM by the person's body weight to get the 1RM kg/Body kg ratio. The Leg press.csv dataset is available from the website. Assuming the data are normally distributed, does this sample provide evidence that the population mean 1RM for leg press is not 2 times a person's body weight? Which of the following is the correct Null hypothesis?

#### Null hypothesis - H0: μ = 2

```{r}
```

## Question 24- State the Alternate Hypothesis

#### Alternate hypothesis - HA μ ≠ 2

```{r}
```

## Question 25 (mod7q25) - What is the sample's mean ratio? (2 dp) [Note: round(x, digits=2)]

```{r}
mod7q25 <- round(mean(leg_press$Ratio, na.rm = TRUE), digits=2)
mod7q25
```

## Question 26 (mod7q26) - What was the sample's standard deviation of the ratio? (2 dp) [Note: round(x, digits=2)]

```{r}
mod7q26 <- round(sd(leg_press$Ratio, na.rm = TRUE), digits=2)
mod7q26
```

## Question 27 (mod7q27) - Calculate the sample's test statistic. (3 dp) [Note: round(x, digits=3)]

```{r}
mod7q27 <- round(t.test(leg_press$Ratio, mu=2, alternative="two.sided")$statistic, digits = 3)
mod7q27
```

## Question 28 (mod7q28_upper) - Upper critical value for the two-tailed Hypothesis test? (3 dp) [Note: round(x, digits=3)]
### Note: df comes from t.test functions
```{r}
mod7q28_upper <- round(qt(p = 0.975, df=19), digits = 3)
mod7q28_upper
```
### Note: Lower (not req. for ans online)
```{r}
mod7q28_lower <- round(qt(p = 0.025, df=19), digits = 3)
mod7q28_lower
```

## Question 29 (mod7q29) - What is the p-value for the Hypothesis test? (3 dp) [Note: round(x, digits=3)]
```{r}
mod7q29 <- round(t.test(leg_press$Ratio, mu=2, alternative="two.sided")$p.value, digits = 3)
mod7q29
```

## Question 30 (mod7q30) - Based on the test statistic and p-value from the Hypothesis test, what was the correct decision?

### One-sample t-sided t-test
### test statistic: -1.722
### p-value: 0.101
### 95 percent confidence interval: 1.689799 2.030201

The p-value approach... (come back)
Test statistic is -1.722, this is interpreted as the sample mean falling 1.722 standard errors (SEs) below the population mean.

```{r}
pt(q = -1.722, df = 19) #ONE TAIL
pt(q = t.test(leg_press$Ratio, mu=2, alternative="two.sided")$statistic, df = 19)

pt(q = -1.722, df = 19)*2 #TWO TAIL
pt(q = t.test(leg_press$Ratio, mu=2, alternative="two.sided")$statistic, df = 19)*2
```
As per the "Confidence Interval Approach"
    If the 95% CI does not capture H0, reject H0
    If the 95% captures H0, fail to reject H0

We fail to reject H0, as H0 = 2
```{r}
mod7q30 <- "*Fail to reject H0*"
```

## Question 31 (mod7q31) - Which of the following conclusions best summarises the results of the Hypothesis test for leg press study?
```{r}
mod7q31 <- "*The results of the study failed to find statistically significant evidence that the population's mean ratio was different to 2.*"
```

## Question 32 (mod7q32) - What is the upper bound of the sample's 95% CI of the mean? (3 dp) [Note: round(x, digits=3)]

```{r}
round(t.test(leg_press$Ratio, conf.level = .95)$conf.int, digits = 3)
```

## Question 33 (mod7q33) - The 95% CI of the sample's ratio captures H0: μ = 2. True or false?
```{r}
mod7q33 <- "True"
```

## Question 34 (mod7q34) - What would be the p-value of the 1RM leg press/body weight kg ratio Hypothesis test if HA: μ < 2 was used? [Note: round(x, digits=3)]
H0:μ=2
HA:μ<3
Alternate hypothesis is stated as a lower one-tail test. One-tailed hypothesis tests predict the alternate hypothesis to be in a specific direction.
```{r}
mod7q34 <- round(t.test(leg_press$Ratio, mu=2, alternative="less")$p.value, digits = 3)
mod7q34
t.test(leg_press$Ratio, mu=2, alternative="less")
```

## Question 35 (mod7q35) - As the Null hypothesised value is captured within the CI, the results of the Hypothesis test are not statistically significant. True or false?

```{r}
mod7q35 <- "*True*"
```

## Question 36 (mod7q36)
```{r}
exer_depr <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1-dsxN6LeMrlpLLQ062iA6H3w9o4XrN1jMjSPkmjmFVA/edit?usp=sharing')
```
A study was conducted to evaluate the effect of strenuous exercise on depression symptoms in a sample of 25 people with major depression. Baseline depression scores were taken from participants using the Beck Depression Inventory (BDI). After one month of strenuous exercise training three times per week, participants rated their depression again using the BDI. The Exercise and depression.csv dataset is available on the website. Researchers want to know if the strenuous exercise program had an impact on depression symptoms. Which of the following statistical tests is most appropriate to answer this question?
```{r}
mod7q36 <- "Paired-samples t-test"
```
When we measure the same sample twice, the measurements are said to be “paired” or “dependent”. Many experiments measure the same people or objects before (baseline) and after (follow-up) a treatment. The paired-samples tt-test, also known as the dependent samples tt-test, is used to check for a statistically significant mean change or difference in these situations. Consider the following example.

## Question 37 - (mod7q37) Which of the following is the correct Null hypothesis to use for the appropriate statistical test for the depression and exercise example?

The population mean of these differences is denoted: μΔ. 
The statistical hypotheses for the paired-samples tt-test are as follows:
  H0:μΔ=0
  HA:μΔ≠0

```{r}
mod7q37 <- "H0:μΔ=0 is the Null Hypothesis for paired sample t-tests"
```

## Question 38 (mod7q38) - Which of the following is the correct Alternate hypothesis to use for the appropriate statistical test for the depression and exercise example?
The population mean of these differences is denoted: μΔ. 
The statistical hypotheses for the paired-samples tt-test are as follows:
  H0:μΔ=0
  HA:μΔ≠0
  
```{r}
mod7q38 <- "HA:μΔ≠0 is the Alternate Hypothesis for paired sample t-tests"
```

## Question 39 (mod7q39) - What was the mean baseline depression score? [Note: round(x, digits=2)]

```{r}
mod7q39 <- round(mean(exer_depr$Baseline, na.rm = TRUE), digits=2)
mod7q39
```

## Question 40 (mod7q40) - What was the mean follow-up depression score? [Note: round(x, digits=2)]

```{r}
mod7q40 <- round(mean(exer_depr$Follow_up, na.rm = TRUE), digits=2)
mod7q40
```

## Question 41 (mod7q41) - What was the mean difference between baseline and follow-up depression scores? [Note: round(x, digits=2)]

```{r}
#Pt 1 - 'Mutate' (calculating detla and adding to dataset)
exer_depr <- exer_depr %>% mutate(delta = Follow_up - Baseline)
```

```{r}
#Pt 2 - Descriptive Statistics
exer_depr %>% summarise(
  Min = min(delta, na.rm = TRUE),
  Q1 = quantile(delta, probs = .25, na.rm = TRUE),
  Median = median(delta, na.rm = TRUE),
  Q3 = quantile(delta, probs = .75, na.rm = TRUE),
  Max = max(delta, na.rm = TRUE),
  Mean = mean(delta, na.rm = TRUE),
  SD = sd(delta, na.rm = TRUE),
  n = n(),
  Missing = sum(is.na(delta))
  )
```

```{r}
#Pt 2 - ALTERNATIVE code
t.test(exer_depr$Follow_up, exer_depr$Baseline, paired = TRUE, alternative = "two.sided")
```
```{r}
#Pt 2 - ALTERNATIVE code
mod7q41 <- round(t.test(exer_depr$Follow_up, exer_depr$Baseline, paired = TRUE, alternative = "two.sided")$estimate, digits = 3)
mod7q41
```

## Question 42 (mod7q42) - Calculate the appropriate test statistic t for the depression and exercise example. [Note: round(x, digits=3)]
```{r}
#Pt 2 - ALTERNATIVE code
mod7q42 <- round(t.test(exer_depr$Follow_up, exer_depr$Baseline, paired = TRUE, alternative = "two.sided")$statistic, digits = 3)
mod7q42
```

## Question 43 (mod7q43) - Upper critical value for the rejection regions of a two-tailed test. [Note: round(x, digits=3)]
### Note: df comes from t.test functions
```{r}
mod7q43_upper <- round(qt(p = 0.975, df=24), digits = 3)
mod7q43_upper
```
```{r}
mod7q43_lower <- round(qt(p = 0.025, df=24), digits = 3)
mod7q43_lower
```
The t∗ values are ±3.949, more extreme than ±2.064, H0 should be rejected. There was a statistically significant mean difference between the before and after.

## Question 44 (mod7q44) - As the test statistic t is more extreme than the critical region cut-off, the Null hypothesis should be REJECTED. True or false?
```{r}
mod7q44 <- "True - The t∗ values are ±3.949, more extreme than ±2.064, H0 should be rejected. There was a statistically significant mean difference between the before and after."
```

## Question 45 (mod7q45) - What is the p-value for the hypothesis test? [Note: round(x, digits=3)]. If the p-value is less than 0.001, enter 0.001.

```{r}
mod7q45 <- round(t.test(exer_depr$Follow_up, exer_depr$Baseline, paired = TRUE, alternative = "two.sided")$p.value, digits = 3)
mod7q45
```

## Question 46 (mod7q46) - Comparing the 0.05 significance level to the p-value, the decision should be to FAIL TO REJECT the Null hypothesis. True or False?





## Question 47 (mod7q47) - 
## Question 48 (mod7q48) - 
## Question 49 (mod7q49) - 
## Question 50 (mod7q50) - 
## Question 51 (mod7q56) - 
## Question 52 (mod7q57) - 
## Question 53 (mod7q58) - 
## Question 54 (mod7q59) - 
## Question 55 (mod7q55) - 
## Question 56 (mod7q56) - 
## Question 57 (mod7q57) - 
## Question 58 (mod7q58) - 
## Question 59 (mod7q59) - 
## Question 60 (mod7q60) - 
## Question 61 (mod7q61) - 
## Question 62 (mod7q62) - 
## Question 63 (mod7q63) - 
## Question 64 (mod7q64) - 

## Question 5 (mod7q5) -
## Question 6
7
8
9
17
18
19
20
21
22





















